---
title: "Covid91 vaccine study Final2021"
author: "iboni archie"
date: "summer 2021"
output: 
    html_document:
          toc: true
          toc_depth: 5
---





```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))

FinalData$treatment <-as.factor(FinalData$treatment)
FinalData$sex <- as.factor(FinalData$sex)                           
FinalData$infected <- as.factor(FinalData$infected)
FinalData$LGBTQ <- as.factor(FinalData$LGBTQ)
FinalData$DrugUser <- as.factor(FinalData$DrugUser)
FinalData$treatment <- relevel(FinalData$treatment,ref="placebo")
FinalData$infected <- relevel(FinalData$infected,ref="OK")
```

```{r}
guy = filter(FinalData,sex == "guy")
gal = filter(FinalData,sex == "gal")
gay = filter(FinalData,LGBTQ == "gay")
yes = filter(FinalData,DrugUser == "yes")
```




# Introduction

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.

# Everyone  

## Barplott

```{r}
barchartGC(~infected + treatment,data=FinalData)
barchartGC(~infected + treatment,data=FinalData, type="percent")

```

```{r}
dd2 <- FinalData %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```







## Numerical results

```{r}
table1 <- xtabs(~infected + treatment, data=FinalData)
table2 <- xtabs(~infected + treatment, data=FinalData)
rowPerc(table1)
colPerc(table1)
```



## Inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
fisher.test(table2)
```




## Now compute effectiveness and print it out.


```{r}
FisherObj  <- fisher.test(table1) 
```


### We extract the odds ratio and compute the effectiveness


```{r}
oddratio = FisherObj$estimate
efft = oddratio/(oddratio+1)
efftness = efft*100
options(digits=3)
```




## The effectiveness is `r efftness`





# Guys

## Barplott



```{r}
barchartGC(~infected + treatment,data=guy)
barchartGC(~infected + treatment,data=guy, type="percent")

```



```{r}
dd2 <- guy %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```











## Numerical results

```{r}
table1 <- xtabs(~infected + treatment, data=guy)
table2 <- xtabs(~infected + treatment, data=guy)
rowPerc(table1)
colPerc(table1)
```

## Inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
fisher.test(table2)
```



## Now compute effectiveness and print it out.


```{r}
FisherObj  <- fisher.test(table1) 
```


### We extract the odds ratio and compute the effectiveness


```{r}
oddratio = FisherObj$estimate
efft = oddratio/(oddratio+1)
efftness = efft*100
options(digits=3)
```




## The effectiveness is `r efftness`






# Gals

## Barplott

```{r}
barchartGC(~infected + treatment,data=gal)
barchartGC(~infected + treatment,data=gal, type="percent")

```




```{r}
dd2 <- gal %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

























## Numerical results

```{r}
table1 <- xtabs(~infected + treatment, data=gal)
table2 <- xtabs(~infected + treatment, data=gal)
rowPerc(table1)
colPerc(table1)
```





## Inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
fisher.test(table2)
```



## Now compute effectiveness and print it out.


```{r}
FisherObj  <- fisher.test(table1) 
```


### We extract the odds ratio and compute the effectiveness


```{r}
oddratio = FisherObj$estimate
efft = oddratio/(oddratio+1)
efftness = efft*100
options(digits=3)
```


## The effectiveness is `r efftness`




# LGBQT

## Barplott 

```{r}
barchartGC(~infected + treatment,data=gay)
barchartGC(~infected + treatment,data=gay, type="percent")

```









## Numerical results

```{r}
table1 <- xtabs(~infected + treatment, data=gay)
table2 <- xtabs(~infected + treatment, data=gay)
rowPerc(table1)
colPerc(table1)
```




## Inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
fisher.test(table2)
```




## Now compute effectiveness and print it out.


```{r}
FisherObj  <- fisher.test(table1) 
```


### We extract the odds ratio and compute the effectiveness


```{r}
oddratio = FisherObj$estimate
efft = oddratio/(oddratio+1)
efftness = efft*100
options(digits=3)
```




## The effectiveness is `r efftness`





# Druguser

## Barplott

```{r}
barchartGC(~infected + treatment,data=yes)
barchartGC(~infected + treatment,data=yes, type="percent")

```










```{r}
dd2 <- yes %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```







## Numerical results

```{r}
table1 <- xtabs(~infected + treatment, data=yes)
table2 <- xtabs(~infected + treatment, data=yes)
rowPerc(table1)
colPerc(table1)
```




## Inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
fisher.test(table2)
```



 

## Now compute effectiveness and print it out.


```{r}
FisherObj  <- fisher.test(table1) 
```


### We extract the odds ratio and compute the effectiveness


```{r}
oddratio = FisherObj$estimate
efft = oddratio/(oddratio+1)
efftness = efft*100
options(digits=3)
```




## The effectiveness is `r efftness`















































  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  













































