---
title: "Covid91 vaccine study Final2021"
author: "iboni archie"
date: "summer 2021"
output: 
    html_document:
          toc: true
          toc_depth: 5
---





```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))

FinalData$treatment <-as.factor(FinalData$treatment)
FinalData$sex <- as.factor(FinalData$sex)                           
FinalData$infected <- as.factor(FinalData$infected)
FinalData$LGBTQ <- as.factor(FinalData$LGBTQ)
FinalData$DrugUser <- as.factor(FinalData$DrugUser)
FinalData$treatment <- relevel(FinalData$treatment,ref="placebo")
FinalData$infected <- relevel(FinalData$infected,ref="OK")
```

```{r}
guy = filter(FinalData,sex == "guy")
gal = filter(FinalData,sex == "gal")
gay = filter(FinalData,LGBTQ == "gay")
yes = filter(FinalData,DrugUser == "yes")
```




# Introduction

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.

# Everyone  

## Barplott

```{r}
barchartGC(~infected + treatment,data=FinalData)
barchartGC(~infected + treatment,data=FinalData, type="percent")

```

```{r}
dd2 <- FinalData %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

In the barplott for everyone shows that the amount of people who got covid from
taking the placebo was 58% compared to the amount of people who took the vaccine
which was around 41% a difference of about 17% which shows the effectiveness of 
of the Vaccine





## Numerical results

```{r}
table1 <- xtabs(~infected + treatment, data=FinalData)
table2 <- xtabs(~infected + treatment, data=FinalData)
rowPerc(table1)
colPerc(table1)
```

relating to the numbers of people who had the vaccine compared to the people who
didnt take the vaccine and got covid the table shows that 42.06 of people who to the covid vaccine and 57.94 of people who took placebo and was exposed contracted the disease.

## Inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
fisher.test(table2)
```

The Pearsons test used to determine the diffrencd between variables
To determine whether the variables are independent, compare the p-value to the significance level. Usually, a significance level of 0.05 works well. A significance level of 0.05 indicates a 5% risk of concluding that an association between the variables exists when there is no actual association.
P-value ≤ α: The variables have a statistically significant association 
If the p-value is less than or equal to the significance level, you reject the null hypothesis and conclude that there is a statistically significant association between the variables.
P-value > α: Cannot conclude that the variables are associated (Fail to reject H0
If the p-value is larger than the significance level, you fail to reject the null hypothesis because there is not enough evidence to conclude that the variables are associated.
In these results, the p-value = 1.3  Because the p-value is greater you accept the null hypothesis. You can conclude that the variables are associated.




## Now compute effectiveness and print it out.


```{r}
FisherObj  <- fisher.test(table1) 
```


### We extract the odds ratio and compute the effectiveness


```{r}
oddratio = FisherObj$estimate
efft = oddratio/(oddratio+1)
efftness = efft*100
options(digits=3)
```




## The effectiveness is `r efftness`





# Guys

## Barplott



```{r}
barchartGC(~infected + treatment,data=guy)
barchartGC(~infected + treatment,data=guy, type="percent")

```



```{r}
dd2 <- guy %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

In the barplott for guys shows that the amount of people who got covid from
taking the placebo was 58% compared to the amount of people who took the vaccine
which was around 41% a difference of about 17% which shows the effectiveness of 
of the Vaccine










## Numerical results

```{r}
table1 <- xtabs(~infected + treatment, data=guy)
table2 <- xtabs(~infected + treatment, data=guy)
rowPerc(table1)
colPerc(table1)
```

relating to the numbers of people who had the vaccine compared to the people who
didnt take the vaccine and got covid the table shows that 58.06 of people who to the covid vaccine and 41.94 of people who took placebo and was exposed contracted the disease.




## Inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
fisher.test(table2)
```

The Pearsons test used to determine the diffrencd between variables
To determine whether the variables are independent, compare the p-value to the significance level. Usually, a significance level of 0.05 works well. A significance level of 0.05 indicates a 5% risk of concluding that an association between the variables exists when there is no actual association.
P-value ≤ α: The variables have a statistically significant association 
If the p-value is less than or equal to the significance level, you reject the null hypothesis and conclude that there is a statistically significant association between the variables.
P-value > α: Cannot conclude that the variables are associated (Fail to reject H0
If the p-value is larger than the significance level, you fail to reject the null hypothesis because there is not enough evidence to conclude that the variables are associated.
In these results, the p-value = 0.6  Because the p-value is greater you have to  accept the null hypothesis. You can conclude that the variables are associated.














## Now compute effectiveness and print it out.


```{r}
FisherObj  <- fisher.test(table1) 
```


### We extract the odds ratio and compute the effectiveness


```{r}
oddratio = FisherObj$estimate
efft = oddratio/(oddratio+1)
efftness = efft*100
options(digits=3)
```




## The effectiveness is `r efftness`






# Gals

## Barplott

```{r}
barchartGC(~infected + treatment,data=gal)
barchartGC(~infected + treatment,data=gal, type="percent")

```




```{r}
dd2 <- gal %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```



In the barplott for women shows that the amount of people who got covid from
taking the placebo was 68% compared to the amount of people who took the vaccine
which was around 36% a difference of about 32% which shows the effectiveness of 
of the Vaccine






















## Numerical results

```{r}
table1 <- xtabs(~infected + treatment, data=gal)
table2 <- xtabs(~infected + treatment, data=gal)
rowPerc(table1)
colPerc(table1)
```

relating to the numbers of people who had the vaccine compared to the people who
didnt take the vaccine and got covid the table shows that 33.06 of people who to the covid vaccine and 66.94 of people who took placebo and was exposed contracted the disease.








## Inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
fisher.test(table2)
```

The Pearsons test used to determine the diffrencd between variables
To determine whether the variables are independent, compare the p-value to the significance level. Usually, a significance level of 0.05 works well. A significance level of 0.05 indicates a 5% risk of concluding that an association between the variables exists when there is no actual association.
P-value ≤ α: The variables have a statistically significant association 
If the p-value is less than or equal to the significance level, you reject the null hypothesis and conclude that there is a statistically significant association between the variables.
P-value > α: Cannot conclude that the variables are associated (Fail to reject H0
If the p-value is larger than the significance level, you fail to reject the null hypothesis because there is not enough evidence to conclude that the variables are associated.
In these results, the p-value = 0.122  Because the p-value is less you reject the null hypothesis. You can conclude that the variables are associated.
























## Now compute effectiveness and print it out.


```{r}
FisherObj  <- fisher.test(table1) 
```


### We extract the odds ratio and compute the effectiveness


```{r}
oddratio = FisherObj$estimate
efft = oddratio/(oddratio+1)
efftness = efft*100
options(digits=3)
```


## The effectiveness is `r efftness`




# LGBQT

## Barplott 

```{r}
barchartGC(~infected + treatment,data=gay)
barchartGC(~infected + treatment,data=gay, type="percent")

```









## Numerical results

```{r}
table1 <- xtabs(~infected + treatment, data=gay)
table2 <- xtabs(~infected + treatment, data=gay)
rowPerc(table1)
colPerc(table1)
```

relating to the numbers of people who had the vaccine compared to the people who
didnt take the vaccine and got covid the table shows that 49.06 of people who to the covid vaccine and 50.8 of people who took placebo and was exposed contracted the disease.







## Inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
fisher.test(table2)
```


The Pearsons test used to determine the diffrencd between variables
To determine whether the variables are independent, compare the p-value to the significance level. Usually, a significance level of 0.05 works well. A significance level of 0.05 indicates a 5% risk of concluding that an association between the variables exists when there is no actual association.
P-value ≤ α: The variables have a statistically significant association 
If the p-value is less than or equal to the significance level, you reject the null hypothesis and conclude that there is a statistically significant association between the variables.
P-value > α: Cannot conclude that the variables are associated (Fail to reject H0
If the p-value is larger than the significance level, you fail to reject the null hypothesis because there is not enough evidence to conclude that the variables are associated.
In these results, the p-value = 0.6 Because the p-value is greater you accept the null hypothesis. You can conclude that the variables are associated.















## Now compute effectiveness and print it out.


```{r}
FisherObj  <- fisher.test(table1) 
```


### We extract the odds ratio and compute the effectiveness


```{r}
oddratio = FisherObj$estimate
efft = oddratio/(oddratio+1)
efftness = efft*100
options(digits=3)
```




## The effectiveness is `r efftness`





# Druguser

## Barplott

```{r}
barchartGC(~infected + treatment,data=yes)
barchartGC(~infected + treatment,data=yes, type="percent")

```










```{r}
dd2 <- yes %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

In the barplott for druguser shows that the amount of people who got covid from
taking the placebo was 62% compared to the amount of people who took the vaccine
which was around 38% a difference of about 24% which shows the effectiveness of 
of the Vaccine






## Numerical results

```{r}
table1 <- xtabs(~infected + treatment, data=yes)
table2 <- xtabs(~infected + treatment, data=yes)
rowPerc(table1)
colPerc(table1)
```

relating to the numbers of people who had the vaccine compared to the people who
didnt take the vaccine and got covid the table shows that 47.8 of people who to the covid vaccine and 52.2 of people who took placebo and was exposed contracted the disease.








## Inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
fisher.test(table2)
```

The Pearsons test used to determine the diffrencd between variables
To determine whether the variables are independent, compare the p-value to the significance level. Usually, a significance level of 0.05 works well. A significance level of 0.05 indicates a 5% risk of concluding that an association between the variables exists when there is no actual association.
P-value ≤ α: The variables have a statistically significant association 
If the p-value is less than or equal to the significance level, you reject the null hypothesis and conclude that there is a statistically significant association between the variables.
P-value > α: Cannot conclude that the variables are associated (Fail to reject H0
If the p-value is larger than the significance level, you fail to reject the null hypothesis because there is not enough evidence to conclude that the variables are associated.
In these results, the p-value = 0.003  Because the p-value is less you reject the null hypothesis. You can conclude that the variables are associated.


















 

## Now compute effectiveness and print it out.


```{r}
FisherObj  <- fisher.test(table1) 
```


### We extract the odds ratio and compute the effectiveness


```{r}
oddratio = FisherObj$estimate
efft = oddratio/(oddratio+1)
efftness = efft*100
options(digits=3)
```




## The effectiveness is `r efftness`















































  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  













































